Diagnosing Simple Wind Models of Cool Gas Outflows as Viewed by Metal-Line Absorption and Emission

### 2010-10-21 Winds/papers/Theory/First/Preprint/windsimple_prpt.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5288 ac11df5e-a788-c23b-a8e1-c758c323924d

\documentclass[12pt,preprint]{aastex}
\usepackage{natbib,amsmath}

@@

\title{Simple Wind Models of Cool Gas Outflows as Viewed by
  Metal-Line Absorption and Emission}

@@

\begin{abstract}
We analyze the absorption and emission-line profiles produced by a set
of simple, cool gas wind models motivated by galactic-scale outflow
observations.  
We implement monte carlo radiative
transfer techniques that track the propagation of scattered and
fluorescent photons to generate 1D spectra and 2D spectral images.
{\bf [Should we make the codes publicly available?  Upon request?]}
%We examine outflows with a range of power-law density and velocity
%profiles and a radiative-driven wind model.  
We focus on the \mgiid\ doublet and \ion{Fe}{2} UV1
multiplet at $\lambda \approx 2600$\AA, but the results are applicable
to other transitions that trace outflows (e.g.\ \ion{Na}{1},
\ion{H}{1} \lya, \ion{Si}{2}).   
By design, the resonance transitions show blue-shifted
absorption but one also predicts strong resonance and fine-structure line-emission at roughly
the systemic velocity.  This line-emission `fills-in' the absorption
reducing the equivalent width by up to $50\%$, shifting the centroid
by tens of \kms, and severely
reducing the effective
opacity near systemic.  Analysis of cool gas outflows that ignores this
line-emission may incorrectly infer that the gas is partially
covered, measure a significantly lower peak optical depth, and/or
conclude that gas at systemic velocity is absent   
(e.g.\ an interstellar or slowly infalling component). 
Because the \ion{Fe}{2} lines
are connected by optically-thin transitions to
fine-structure levels, their profiles
more closely reproduce the intrinsic opacity
of the wind.   Together these results naturally explain the
absorption and emission-line characteristics observed for star-forming
galaxies at $z<1$.
We also study a scenario purported to describe the outflows
of $z \sim 3$ Lyman break galaxies and argue this model fails to
reproduce the observations when radiative transfer of scattered photons
is properly considered.   
%Strong line-emission from metal-line
%transitions is a generic prediction of wind models, even in the
%presence of dust and anisotropic configurations.  
Although line-emission complicates the analysis of absorption-line
profiles, the 
surface brightness profiles 
offers a unique means of assessing the morphology and size
of galactic-scale winds.  Furthermore, the kinematics and line-ratios
offer powerful diagnostics of outflows,  motivating deep,
spatially-extended spectroscopic observations.

@@

For our 3-dimensional calculations, the  wind properties (density, temperature and velocity) were discretized on a $300^3$ Cartesian grid (for certain 1-D calculations, the wind properties were simply computed on the fly from analytic formulae).   
The radiation field was represented by $N$ photon packets (typically $N \sim 10^7$) which were initially emitted isotropically and uniformly throughout the source region ($r < r_{\rm source}$).  The wavelengths of the packets were sampled from a flat spectral energy distribution.

@@

We have also analyzed the predicted profiles for a series of biconical
winds with $\theta = 10-60^\circ$, each viewed along the axis of
asymmetry with the wind covering the source.
Table~\ref{tab:line_diag} summarizes the results for two cases.  For
modest opening angles $\theta < 20^\circ$, the results are
qualitatively similar to the fiducial model;  the profiles show
similar equivalent widths for absorption and emission.  The key
quantitative difference is that the \feiis\ line-emission is
suppressed at $\delta v \approx 0 \mkms$ because the portion of the
wind with that projected velocity has been removed.  For
$\theta>45^\circ$, enough of the wind has been removed that the
line-emission is several times weaker than the fiducial model.
Similarly, the absorption-line profiles more closely track the
intrinsic optical depth of the outflow.   Of course, these same models
when viewed `sideways' would show no absorption yet significant
line-emission.  Such events are sufficiently rare (Rubin et
al., in prep) that we consider this level of anisotropy to be of minor
importance.

@@

The differences in the \ion{Fe}{2} absorption profiles are reflected
in the much higher strengths ($3-10\times$) of emission from
transitions to the excited states of the \aconfig\ configuration.   This occurs because:
(1) there is greater absorption by the \feiid\
resonance lines; (2) the high opacity of the ISM component leads to
an enhanced conversion of resonance photons with $\mdv \approx 0\mkms$
into \feiis\ photons.  This is especially notable for the
\feiib\ transition whose coupled \feiis\ transition shows an equivalent width nearly
$10\times$ stronger than for the fiducial model.  The relative
strengths of the \feiib\ and \feiie\ lines provide a direct
diagnostic on the degree to which the resonance line photons are
trapped, i.e.\ the peak optical depth of \ion{Fe}{2}~2600 and
the velocity gradient of the wind.

@@

Another factor that may reduce line-emission is an
anisotropic wind model. The flux is lower, for example, if one
eliminates the backside to the wind (e.g.\ the source itself could
shadow a significant fraction of the backside).  
Similarly, 
many of the scattered photons of the fiducial 
model arise nearly normal to the sightline such that a biconical
wind can have significantly lower line-emission
($\S$~\ref{sec:anisotropic}). 
For the anisotropic winds explored in this paper,
the line-emission scales 
roughly as $\Omega/4\pi$ where $\Omega$ is the angular extent of the
wind\footnote{There is also a first order dependence on the actual
  orientation of the wind, with maximal emission when the backside is
  fully viewed.}.  Because we require that the wind 
points toward us, it is difficult to reduce $\Omega$ much
below $2 \pi$ and, therefore, anisotropy reduces the
emission by a factor of order unity.  
Similarly, an anisotropically emitting source would modify the predicted
line-emission.  For example, if the backside of the galaxy were
brighter/fainter then would one predict brighter/fainter emission
relative to the observed continuum.
To reduce the emission, the brightest regions
of the galaxy would need to be oriented toward Earth.  Although this
would not be a
generic orientation, most spectroscopic samples are magnitude-limited
and biased towards detecting galaxies when observed at their
brightest.  In principle, this might imply a further
reduction of order unity.

@@

The most obvious measures provided by the line-emission are
estimates
of the size and morphology of the outflow \citep{rubin+10c}.  
Line emission is predicted to extend to radii where the Sobolev
optical depth exceeds a few tenths.  The principle
challenge is to achieve sufficient sensitivity to detect the predicted
low
surface brightness emission. As Figure~\ref{fig:obs_sb}
demonstrates, the surface brightness at the inner wind radius of our
fiducial wind exceeds that at the outer radius by several orders of magnitude.
Nevertheless, an instrument that sampled the entire wind (e.g.\ a
large format IFU or narrow band imager) may detect the emission in
azimuthally averaged apertures. 
For the fiducial wind model, for example, the azimuthally integrated
flux falls by only a factor of 10 for projected radii of 1 to 15\,kpc.
Of the transitions considered in this paper, \ion{Mg}{2} emission is
preferred for this analysis because 
(i) it has the largest equivalent width in absorption and
(ii) there are fewer emission channels per absorption line than for
\ion{Fe}{2}.  The \ion{Mg}{2} lines (especially \mgiib) frequently has the
highest peak and integrated fluxes (Figure~\ref{fig:obs_sb}).  
On the other hand, the \ion{Mg}{2} transitions are more susceptible to
the effects of dust extinction and for some galaxies \feiis\ emission
could be dominant.  In either case, the study of spatially-extended
line-emission from photons scattered by the galactic-scale wind offers
an direct means to study the morphology and radial extent of these
phenomena.  The next generation of large-format optical and infrared
integral-field-units are well-suited to this scientific endeavor
(e.g.\ KCWI on Keck, MUSE on the VLT).

@@

The emission-line velocity widths also reveal
characteristics of the wind.  In particular, the \feiis\ emission-line 
widths are
sensitive to the optical depth of the wind at large velocities from
systemic.  This is illustrated in Figure~\ref{fig:obs_edelv} which plots
the 90\%\ velocity width $\Delta v_e$ of \feiic\ versus the velocity
where the wind optical depth is maximal ($v_\tau$).  We find that
$\Delta v_e$ increases with $v_\tau$ such that a large width for
\feiis\ emission requires a wind profile with large optical depths at
$\mdv < -200 \mkms$.  The broadening of \feiis\ emission occurs
because this emission is dominated by single scatterings 
which trace all components of the wind.

Lastly, the line flux ratios of pairs of transitions 
are sensitive to characteristics of the wind.
The most obvious example is the relative emission of the \mgiid\
doublet.  Specifically, an outflow whose velocity exceeds the doublet
spacing ($\Delta v \approx 770 \mkms$) will convert \mgiia\ photons
into \mgiib\ emission resulting in a flux ratio that is inverted
relative to the intrinsic optical depth profiles (e.g.\
Figure~\ref{fig:norm}).  Another important example is the relative
flux of \feiis\ emission relative to \ion{Mg}{2}.  
A dusty medium with velocity near systemic (e.g.\ an
ISM component) may significantly suppress \ion{Mg}{2} emission yet
have a significant \feiis\ line flux because the latter is not
resonantly trapped.

@@

In this paper, we have explored the predicted absorption and
emission-line profiles of a set of simple galactic-scale outflow
models.  Our analysis focused on the \mgiid\ and \ion{Fe}{2} UV1
multiple of rest-frame UV transitions, but the results transfer to
most other lines used to probe cool gas.  Our primary
findings are summarized as follows:

@@

\item Isotropic, dust-free wind models conserve photon flux.
  Therefore, the blue-shifted absorption-line profiles commonly
  observed in star-forming galaxies are predicted to be accompanied by
  emission-lines with similar equivalent width.  This even holds for
  non-extreme anisotropic and dust-extincted scenarios.

\item The line-emission occurs preferentially at the systemic velocity
  of the galaxy and `fills-in' the absorption profiles at velocity
  offsets $|\mdv| < 200 \mkms$ from systemic.  For transitions that
  are only coupled to the ground-state (e.g.\ \ion{Mg}{2}, \lya,
  \ion{Na}{1}),  this implies much lower equivalent widths (up to
  $50\%$) and also velocity profiles that are significantly offset
  from the intrinsic optical depth profile.

@@

\item Resonance transitions that are strongly coupled to
non-resonant lines (e.g.\ \ion{Fe}{2}, \ion{Si}{2}) 
produce emission dominated by the
optically-thin, fine-structure transitions.  As such, the resonance
absorption lines offer the best
characterization of the opacity of the wind and also of material 
with velocities near systemic.

\item  Dust extinction modestly affects 
  models where resonance photons are trapped for only a few scatterings.  Models
  with high opacity at small radii and at systemic velocity (e.g.\ an
  optically thick, ISM component)  can effectively extinguish
  resonantly trapped emission (\ion{Mg}{2}) but have more modest
  effect on non-resonant lines (\feiis).

\item We examined two scenarios designed to mimic the wind model
  proposed by S10 for $z \sim 3$ Lyman break galaxies.  These models
  predict substantial line-emission from scattered photons that
  greatly modify the predicted line-profiles so that  
  these models do not reproduce the observed line-profiles.

@@

\item Significant line-emission is a generic prediction of simple wind
  models, even in the presence of dust, anisotropic flows, and when
  viewed through finite apertures.  We have explored the 2D emission
  maps (Figure~\ref{fig:fiducial_ifu_mgii}) and surface brightness 
  profiles (Figure~\ref{fig:obs_sb}) of
  the winds.  Sensitive, spatially-extended observations will map the
  morphology and radial extent of the outflows.  These data afford the
  best opportunity to estimate the energetics and mass-flux of
  galactic-scale outflows.

\item The kinematics and flux ratios of the emission lines 
  constrain the wind speed, opacity, dust extinction, and morphology of the
  wind.

@@

We acknowledge valuable conversations with D. Koo, J. Hennawi, and
A. Wolfe. 
J.X.P and K.R. are partially supported
by an NSF CAREER grant (AST--0548180), and 
by NSF grant AST-0908910.

>>>>

\documentclass[]{emulateapj}
%\documentclass[12pt,preprint]{aastex}
\usepackage{natbib,amsmath}

@@

\title{Diagnosing Simple Wind Models of Cool Gas Outflows as Viewed by
  Metal-Line Absorption and Emission}

@@

\begin{abstract}
We analyze the absorption and emission-line profiles produced by a set
of simple, cool gas wind models motivated by galactic-scale outflow
observations.  
We examine outflows with a range of power-law density and velocity
profiles and a radiative-driven wind model.  
We focus on the \mgiid\ doublet and \ion{Fe}{2} UV1
multiplet at $\lambda \approx 2600$\AA, but the results are applicable
to other transitions that trace outflows (e.g.\ \ion{Na}{1},
\ion{H}{1} \lya, \ion{Si}{2}).   We implement monte carlo radiative
transfer techniques that track the propogation of scattered and
flourescent photons to generate 1D spectra and 2D spectral images.
[Should we make the codes publically available?  Upon request?]
[Mention fiducial model here?]
As expected, the \ion{Mg}{2} doublet exhibits strong, blue-shifted
absorption but one also predicts strong line-emission at roughly
the systemic velocity.  This line-emission `fills-in' the absorption, 
significantly reducing the effective
opacity near systemic. Analysis of cool gas outflows that entirely ignores this
line-emission may incorrectly infer that the gas is partially
covered, measure a significantly lower peak optical depth, and/or
conclude that gas at systemic velocity is absent   
(e.g.\ an ISM or slowly infalling component). 
The \ion{Fe}{2} resonance lines show similar behaviour, however 
these lines are connected to optically thin transitions to
fine-structure levels. As such, the \ion{Fe}{2} 
absorption lines more faithfully reproduce the intrinsic opacity
of the wind.   Together these results naturally explain the
absorption and emission-line characteristics observed for star-forming
galaies at $z<1$.
We also study a scenario purported to describe the outflows
of $z \sim 3$ Lyman break galaxies and argue this model fails to
reproduce the observations when (previously ignored) scattered photons
are properly considered.   
%Strong line-emission from metal-line
%transitions is a generic prediction of wind models, even in the
%presence of dust and anisotropic configurations.  
The surface brightness profiles of emission from metal-line
transitions offers a unique means of assessing the morphology and size
of galactic-scale winds motivating deep,
spatially-extended spectroscopic observations.

@@

For our 3-dimensional calculations, the  wind properties (density, temperature and velocity) were descritized on a $300^3$ Cartesian grid (for certain 1-D calculations, the wind properties were simply computed on the fly from analytic formulae).   
The radiation field was represented by $N$ photon packets (typically $N \sim 10^7$) which were initially emitted isotropically and uniformly throughout the source region ($r < r_{\rm source}$).  The wavelengths of the packets were sampled from a flat spectral energy distribution.

@@

[Add a paragraph on the bi-conical wind once we are confident in the
results.  This may be a rather big effect.]

[Consider showing a 2D model for biconical]

@@

The differences in the \ion{Fe}{2} absorption profiles are reflected
in the much higher strengths ($3-10\times$) of emission from
transitions to the excited states of the \aconfig\ configuration.   This occurs because:
(1) there is greater absorption by the \feiid\
resonance lines; (2) the high opacity of the ISM component leads to
an enhanced conversion of resonance photons with $\mdv \approx 0\mkms$
into \feiis\ photons.  This is especially notable for the
\feiib\ transition whose coupled \feiis\ transition shows an equivalent width nearly
$10\times$ stronger than for the fiducial model.  The relative
strengths of the \feiib\ and \feiie\ lines provide a direct
diagnostic on the degree to which the resonance line photons are
trapped, i.e.\ the peak opitcal depth of \ion{Fe}{2}~2600 and
the velocity gradient of the wind.

@@

Another factor that may reduce line-emission is a
non-isotropic wind model. The flux is lower, for example, if one
eliminates the backside to the wind (e.g.\ the source itself could
shadow a significant fraction of the backside).  
For our fiducial model, many of the photons scattered into our
sightline arise nearly normal to the sightline such that a biconicial
wind has significantly lower line-emission
($\S$~\ref{sec:anisotropic}). 
For the anisotropic winds explored in this paper,
the line-emission scales 
roughly as $\Omega/4\pi$ where $\Omega$ is the angular extent of the
wind\footnote{There is also a first order dependence on the actual
  orientation of the wind, with maximal emission when the backside is
  fully viewed.}.  Because we require that the wind 
points toward us, it is difficult to reduce $\Omega$ much
below $2 \pi$ and, therefore, anisotropy reduces the
emission by a factor of order unity.  
Similarly, an anisotropically emitting source would modify the predicted
line-emission.  For example, if the backside of the galaxy were
brighter/fainter then would one predict brighter/fainter emission
relative to the observed continuum.
To reduce the emission, the brightest regions
of the galaxy would need to be oriented toward Earth.  Although this
would not be a
generic orientation, most spectroscopic samples are magnitude-limited
and biased towards detecting galaxies when observed from their
brightest viewpoint.  In principle, this might imply a further
reduction of order unity.
{\bf [Put comments on biconical here]}

@@

The most obvious measures provided by the line-emission are
estimates
of the size and morphology of the outflow \citep{rubin+10c}.  
Line emission is predicted to extend to radii where the Sobolev
optical depth exceeds a few tenths.  The principle
challenge is to achieve sufficient sensitivity to detect the predicted
low
surface brightness emission. As Figure~\ref{fig:obs_sb}
demonstrates, the surface brightness at the inner wind radius of our
fiducial wind exceeds that at the outer radius by several orders of magnitude.
Nevertheless, an instrument that sampled the entire wind (e.g.\ a
large format IFU or narrow band imager) may detect the emission in
azimuthally averaged apertures. 
For the fiducial wind model, for example, the azimuthally integrated
flux falls by only a factor of 10 for projected radii of 1 to 15\,kpc.
Of the transitions considered in this paper, \ion{Mg}{2} emission is
preferred for this analysis because 
(i) it has the largest equivalent width in absorption and
(ii) there are fewer emission channels per absorption line than for
\ion{Fe}{2}.  The \ion{Mg}{2} lines (especially \mgiib) frequently has the
highest peak and integrated fluxes (Figure~\ref{fig:obs_sb}).  
On the other hand, the \ion{Mg}{2} transitions are more susceptible to
the effects of dust extinction and for some galaxies \feiis\ emission
could be dominant.  In either case, the study of spatially-extended
line-emission from photons scattred by the galactic-scale wind offers
an direct means to study the morphology and radial extent of these
phenomena.  The next generation of large-format optical and infrared
integral-field-units are well-suited to this scientific endeavor
(e.g.\ KCWI on Keck, MUSE on the VLT).

@@

The emission-line velocity widths also reveal
characteristics of the wind.  In particular, the \feiis\ emission-line 
widths are
sensitive to the optical depth of the wind at large velocities from
systemic.  This is illustrated in Figure~\ref{fig:obs_edelv} which plots
the 90\%\ velocity width $\Delta v_e$ of \feiic\ versus the velocity
where the wind optical depth is maximal ($v_\tau$).  We find that
$\Delta v_e$ increases with $v_\tau$ such that a large width for
\feiis\ emission requires a wind profile with large optical depths at
$\mdv < -200 \mkms$.  The broadening of \feiis\ emission occurs
because this emission is dominated by single scatterings 
which trace all components of the wind.  {\bf [Also the optical depth profile of
  FeII]}

Lastly, the line flux ratios of pairs of transitions 
are sensitive to characteristics of the wind.
The most obvious example is the relative emisison of the \mgiid\
doublet.  Specifically, an outflow whose velocity exceeds the doublet
spacing ($\Delta v \approx 770 \mkms$) will convert \mgiia\ photons
into \mgiib\ emission resulting in a flux ratio that is inverted
relative to the intrinsic optical depth profiles (e.g.\
Figure~\ref{fig:norm}).  Another important example is the relative
flux of \feiis\ emission relative to \ion{Mg}{2}.  
A dusty medium with velocity near systemic (e.g.\ an
ISM component) may significantly suppress \ion{Mg}{2} emission yet
have a significant \feiis\ line flux because the latter is not
resonantly trapped.

@@

In this paper, we have explored the predicted absorption and
emission-line profiles of a set of simple galactic-scale outflow
models.  Our analysis focused on the \mgiid\ and \ion{Fe}{2} UV1
multiple of rest-frame UV transitions, but the results translate to
most other transitions used to probe cool gas.  Our primary
findings are summarized as follows:

@@

\item Isotropic, dust-free wind models conserve photon flux.
  Therefore, the blue-shifted absorption-line profiles commonly
  observed in star-forming galaxies are predicted to be accompanied by
  emission-lines with similar equivalent width.  This is even true for
  anisotropic and dust-extincted scenarios.

\item The line-emission occurs preferentially at the systemic velocity
  of the galaxy and `fills-in' the absorption profiles at velocity
  offsets $|\mdv| < 200 \mkms$ from systemic.  For transitions that
  are only coupled to the ground-state (e.g.\ \ion{Mg}{2}, \lya,
  \ion{Na}{1}). The observed absorption profiles may be significantly
  different from the intrinsic optical depth profile.

@@

\item Resonance transitions that are strongly coupled to
non-resonant lines (e.g.\ \ion{Fe}{2}, \ion{Si}{2}) offer the best
characterization of the opacity of the wind and also material 
with velocities near systemic.  The emission will generally be dominated by the
optically-thin, fine-structure transitions.

\item  Dust extinction has only modest effects 
  in models which predict only a few scatterings.  Models
  with high opacity at small radii and at systemic velocity (e.g.\ an
  optically thick, ISM component)  can effectively extinguish
  resonantly trapped emission (\ion{Mg}{2}) but have more modest
  effect on non-resonant lines (\feiis).

\item We examined two scenarios designed to mimic the wind model
  proposed by S10 for $z \sim 3$ Lyman break galaxies.  These models
  predict substantial line-emission from scattered photons that
  greatly modify the predicted line-profiles.  
  These models do not reproduce the observed line-profiles.

@@

\item The kinematics and flux ratios of the emission lines 
  constrain the wind speed, opacity, dust extinction, and XXX of the
  wind.

\item Biconical?

\item Significant line-emission is a generic prediction of simple wind
  models, even in the presence of dust, anisotropic flows, and when
  viewed through finite apertures.  We have explored the 2D emission
  maps (Figure~\ref{fig:ifu}) and surface brightness profiles (Figure~\ref{fig:obs_sb}) of
  the winds.  Sensitive, spatially-extended observations will map the
  morphology and radial extent of the outflows.  These data afford the
  best opportunity to estimate the energetics and mass-flux of
  galactic-scale outflows.

@@

We acknowledge valuable conversations with D. Koo, J. Hennawi, and ... 
J.X.P and K.R. are partially supported
by an NSF CAREER grant (AST--0548180), and 
by NSF grant AST-0908910.

\begin{figure}[ht]
%\epsscale{0.95}
%\plotone{../Figures/energy_levels.ps}
\centering
\includegraphics[width=3.5in]{../Figures/energy_levels.ps}
\caption{
Energy level diagrams for the \mgiid\ doublet and the UV1
multiplet of \ion{Fe}{2} transitions   
(based on Figure~7 from \cite{hmt+99}).
Each transition shown is
labeled by its rest wavelength (\AA) and Einstein A-coefficient
(s$^{-1}$). Black upward arrows
indicate the resonance-line transitions, i.e.\ those connected to the ground
state.  The 2p$^6$3p configuration of Mg$^+$ is split into
two energy levels that give rise to the \mgiid\ doublet.  
Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
exhibit fine-structure splitting that gives rise to a series of
electric-dipole transitions. 
The downward (green) arrows show the \feiis\ transitions that are connected to the
resonance-line transitions (i.e.\ they share the same upper energy
levels).  We also show a pair of levels (\ion{Fe}{2}$^* \lambda\lambda
2618,2631$; red and dashed lines) that arise from higher levels in the \zconfig\
configuration.  These transitions have not yet been observed in
galactic-scale outflows and are not considered in our analysis.
}
\label{fig:energy}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.5in]{../Figures/oneline_test.eps}
%\epsscale{0.8}
%\plotone{../Figures/oneline_test.eps}
\caption{
Line profiles of a test problem calculated using the monte carlo code (solid) and by direct numerical integration of the transport equation under the Sobolev approximation (dashed lines).  The configuration was  spherical and consisted of a homologously expanding wind  with density profile $n \propto r^{-2}$  lying above an opaque emitting surface at velocity coordinate 100~km~s$^{-1}$.  
The wind extended to 2,000 km~s$^{-1}$ and the Sobolev optical depth had values of  $\tau = 1$ (black lines), $\tau = 10$ (red lines), and $\tau = 100$ (blue lines).    Discrepancies in the $\tau = 100$ case are likely due to the breakdown of the Sobolev approximation at high optical depth. 
}
\label{fig:oneline_test}
\end{figure}

\begin{figure}
%\epsscale{0.8}
\includegraphics[height=3.5in,angle=90]{../Figures/fig_nvtau_vs_r.ps}
\caption{
Density (dashed; red), radial velocity (dotted; blue), and
\mgiia\ optical depth profiles (solid and dotted; black) for the fiducial
wind model (see Table~\ref{tab:fiducial} for details).
The density and velocity laws are simple $r^{-2}$ and $r^1$
power-laws; these curves have been scaled for plotting
convenience.  
The optical depth profile was calculated two ways: (i) using the
Sobolev approximation (Equation~\ref{eqn:Sobolev}; solid black curve)
and (ii) summing
the opacity at small and discrete radial intervals in velocity space
and then converting to radius with the velocity law.  These give
very similar results. One notes that
the wind is optically thick at the inner radius ($r_{\rm inner} =
1$\,kpc) and becomes optically thin at the outer radius ($r_{\rm
  outer} = 20$\,kpc).
}
\label{fig:fiducial_nvt}
\end{figure}

\begin{figure*}
\includegraphics[scale=0.6,angle=90]{../Figures/fig_fiducial_1d.ps}
\caption{
{\it Left} -- (Upper) \mgiid\ profiles for the fiducial wind model
described in Table~\ref{tab:fiducial} and
Figure~\ref{fig:fiducial_nvt}.  The doublet shows the P-Cygni profiles
characteristic of an outflow with significant absorption blueward of
line-center (dashed vertical lines) extending to $v = -1000\mkms$
and significant emission redward of line-center.  Note
that even though the peak optical depth of the \ion{Mg}{2} transitions
is $\tau_{2796}^{\rm max} \approx 30$ at $v \approx -70 \mkms$,
photons scattered off the outflow significantly fill-in the absorption.
(Lower) \ion{Fe}{2} absorption and emission profiles for the UV1
multiplet at $\lambda \approx 2600$\AA.  The \feiid\ resonance lines 
show weaker absorption due to the smaller Fe$^+$ number density and
lower $f\lambda$ values.  Each also shows a P-Cygni profile, although
the emission for \feiia\ is much weaker than that for the
\feiib\ and \mgiid\ transitions.  This is because a majority of the
absorbed \feiia\ photons fluoresce into
\ion{Fe}{2}$^*~\lambda\lambda 2612, 2632$ photons.
{\it Right} -- A subset of the transitions displayed in a velocity
plot.
}
\label{fig:fiducial_1d}
\end{figure*}

\begin{figure}
%\epsscale{0.8}
\includegraphics[width=3.5in]{../Figures/fig_noemiss.ps}
\caption{
The solid curves show the line profiles (absorption and emission) of
the \ion{Mg}{2} and \ion{Fe}{2} resonance lines for the fiducial wind
model.  These include the effects of scattered photons and show the
canonical P-Cygni profiles of a source 
embedded within an outflow.  Overplotted on each transition (dotted line) is
the predicted absorption profile under the constraint that every
absorbed photon is lost from the system, i.e.\ no scattering or
re-emission occurs.   The true profiles have been `filled-in' 
significantly by light scattered in the wind.  Ignoring this
process, one would model the absorption lines with a systematically lower
optical depth and (incorrectly) conclude that the source is partly covered by the
gas.  
}
\label{fig:noemiss}
\end{figure}

\begin{figure}
%\epsscale{0.8}
\includegraphics[width=3.5in]{../Figures/fig_fiducial_ifu_mgii.ps}
\caption{
Surface-brightness emission maps around the \mgiia\ transition for the
source+wind complex of the fiducial model.  The middle panel shows the
1D spectrum with $v=0 
\mkms$ corresponding to $\lambda = 2796.35$\AA\ and the dotted vertical
curves indicate the velocity slices for the emission maps.  The
source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
pixels at the center of each map.   At $v=-250 \mkms$, the wind has an optical
depth of $\tau_{2796} \approx 1$ and the source contributes
roughly half of the observed flux.  At $v=-100 \mkms$ the
wind absorbs all photons from the source and the observed emission is
entirely due to photons scattered by the wind.  Impressively, this
emission exceeds the integrated flux at $v = -250\mkms$ such that the
\mgiia\ line center is offset from the (intrinsic) peak in optical depth.  At $v \ge 0
\mkms$,  both the source and wind contribute to the observed emission.
At all velocities, the majority of emission comes from the inner
$\approx 5$\,kpc.
}
\label{fig:fiducial_ifu_mgii}
\end{figure}

\begin{figure}
\includegraphics[width=3.5in]{../Figures/fig_feii_ifu.ps}
\caption{
(Upper) Surface-brightness emission maps around the \feiib\ transition for the
source+wind complex.  
%The middle panel shows the 1D spectrum with $v=0
%\mkms$ corresponding to $\lambda = 2600.173$\AA\ and the dotted vertical
%curves indicating the velocity slices for the emission maps.  
The results are very similar to those observed for the \mgiid\ doublet
(Figure~\ref{fig:fiducial_ifu_mgii}).
(Lower) Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda
2612$ transition for the 
source+wind complex.  %The middle panel shows the 1D spectrum with $v=0
%\mkms$ corresponding to $\lambda = 2612.654$\AA\ and the dotted vertical
%curves indicating the velocity slices for the emission maps.  
In this case, the source is unattenuated yet scattered photons from
the wind also make a significant contribution. 
[Is this figure superfluous??]
}
\label{fig:fiducial_ifu_feii}
\end{figure}

\begin{figure}
\includegraphics[width=3.5in]{../Figures/fig_asymm_spec.ps}
\caption{
Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
case (black lines) compared against an anisotropic wind blowing into
only $2\pi$ steradians as viewed from $\phi = 0^\circ$ (source
uncovered) to $\phi = 180^\circ$ (source covered).  One detects
significant emission for all orientations of this wind but significant
absorption only for $\phi \ge 90^\circ$.
The velocity centroid of the 
emission shifts from positive to negative velocities as $\phi$
increases and one transitions from viewing the wind to be behind the
source to in front.  The velocity centroid of emission, therefore, may
give a robust measure of wind isotropy.
}
\label{fig:anisotropic}
\end{figure}

\begin{figure}
\includegraphics[width=3.5in]{../Figures/fig_dust_spec.ps}
\caption{
Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
model (black) against a series of models that include 
dust extinction.  The primary effect is suppression of
the line-emission relative to the continuum. 
A more subtle but important effect is that the redder photons in the
emission lines (corresponding to higher velocity relative to
line-center) suffer greater extinction.  This is most evident in the
\feiic\ emission line; it occurs because these photons must
travel farther to scatter off the backside of the wind.  Note that
the absorption lines are nearly unmodified until $\mtaud = 10$, a
level of extinction that would preclude observing the source
altogether.
}
\label{fig:dust}
\end{figure}

\begin{figure}
\epsscale{0.8}
\includegraphics[height=3.5in,angle=90]{../Figures/fig_taud_vs_we.ps}
\caption{
Predicted line-emission equivalent widths for \mgiib\ from the
fiducial wind model, as attenuated by dust with a range of \taud\
values.  
It is obvious that the equivalent widths (i.e., the flux relative to
the continuum) do not scale as $\exp(\tau_d)$.
The black (solid) curve shows the model predictions while the
dotted (red) line plots $W_{\rm e}(\tau_d) = W_{\rm e}(\tau_d = 0)
\cdot (1+\tau_d)^{-1}$.  This simple approximation is a good
representation of the radiative transfer results.   
}
\label{fig:dust_tau}
\end{figure}

\begin{figure}
\includegraphics[width=3.5in]{../Figures/fig_ism_spec.ps}
\caption{
Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the ISM+wind
model (red) compared against the fiducial wind model (black). 
The dotted line traces the predicted absorption profile in the absence
of re-emission and scattering.
Regarding the \ion{Mg}{2}~doublet, the primary difference between the
ISM+wind and the fiducial models is the shift of $\approx 100 \mkms$
in the emission lines from $v \approx 0 \mkms$ for the fiducial
model to $v \approx +100\mkms$ for the ISM+wind model. 
The \ion{Fe}{2} profiles, meanwhile, show several qualitative differences. 
The \feiid\ resonance transitions each exhibit much
greater absorption at $v \approx 0 \mkms$ than the fiducial model.
The resonant line-emission is also substantially
reduced, implying much higher fluxes for the non-resonant lines (e.g.\
\feiic,2626).  The lack of scattered \feiia\ photons results in an
absorption profile that very nearly matches the input opacity profile.
We conclude that resonance transitions that are strongly coupled to
non-resonant lines offer the best
characterization of an ISM component.
}
\label{fig:ISM_spec}
\end{figure}

\begin{figure}
\includegraphics[width=3.5in]{../Figures/fig_norm_spec.ps}
\caption{
\ion{Mg}{2} and \ion{Fe}{2} profiles for the fiducial model with
varying normalization, parameterized by \nhn.  As expected, the
strength of absorption increases with increasing \nhn\ which also
results in stronger line-emission.  Note that the \feiia\ emission is
always weak; only its absorption increases with \nhn\ and actually exceeds
the depth of \feiib\ for $\mnhn > \mnhf$.  The depth of the
\ion{Mg}{2} doublet, meanwhile, always falls below a relative flux of
0.3 while the \mgiib\ emission rises steadily with \nhn.
}
\label{fig:norm}
\end{figure}

\begin{figure}
\includegraphics[width=3.5in]{../Figures/fig_lbg_sobolev.ps}
\caption{
(a) The dotted curve shows the velocity law (values are labeled on the
right side) for the LBG model
of S10.  Note how rapidly the velocity rises from $r =
1$ to 2\,kpc.  The solid curve shows the Sobolev solution for the
Mg$^+$ gas
density derived from 
the average absorption profile of LBG galaxies (see below).
The density drops off as $(r/{\rm kpc}-1)^{-0.6}$ initially and then
steepens to $(r/{\rm kpc}-1)^{-1.8}$.
(b) The average profile for LBG cool gas absorption as
measured and defined by S10
(black solid curve).  Overplotted on this curve is a (red) dotted line that
shows the \mgiia\ absorption profile derived from the density (and velocity)
law shown in the upper panel.  
}
\label{fig:LBG_Sobolev}
\end{figure}

\begin{figure}
\includegraphics[width=3.5in]{../Figures/fig_lbg_spec.ps}
\caption{
Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the two
LBG models considered: (red) the profiles from the 
Sobolev approximation 
and (black) a model constructed to faithfully
correspond to the wind model advocated by S10.  The dotted line
shows the absorption profiles of the latter model if one were
to neglect scattered and re-emitted photons.  Similar to the fiducial
model (Figure~\ref{fig:fiducial_1d}), scattered and re-emitted photons
significantly modify the absorption profiles (especially \ion{Mg}{2}
and \feiib)
and produce significant emission lines.  
The result, for \ion{Mg}{2} especially, is a set of profiles that do
not match the average observed LBG absorption profile.
}
\label{fig:LBG_spec}
\end{figure}
